---
title: lyricRipples
author: "Amy Holt"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## This the early plan for functions for lyricRipple
LyricRipples is an R package to analyze and compare lyrical themes 
and sentiments across different generations of music artists. The project will 
focus on identifying changes in themes, emotions, and word usage from Generation 
X (1965–1980), Millennials (1981–1996), and Generation Z (1997–2012), revealing 
insights into cultural and generational shifts.


```{r}
# load the packages
#library(usethis)
#library(devtools)
#library(roxygen2)
#library(testthat)
#install.packages("geniusr","rvest", "stringr", "topicmodels")
#library(geniusr)
#library(rvest)
#library(stringr)
#library(tidytext)
#library(topicmodels)
#library(tm)
#library(textdata)
#library(ggplot2)
#library(wordcloud2)
#library(RColorBrewer)
```

## Lyric Scraping

Lyrics will be scraped 

```{r}
lyrics <- function(artist){
  # Code using API to retrieve lyrics
}
```

## Sentiment Analysis
Sentiment Scoring: Use tidytext with the either bing or nrc lexicons for 
emotional tone analysis. Create a function to generate sentiment scores for 
each lyric line or song. 
```{r}

analyze_sentiment <- function(lyrics) {
    lyrics %>%
    unnest_tokens(word, lyrics) %>%
    inner_join(get_sentiments("nrc")) %>%
    count(sentiment, sort = TRUE)
}

```

## Word Frequency Analysis
Generate term frequency distributions for each artist and generation, 
filtering stop words and common words.


```{r}
word_freq <- function(lyrics) {
    lyrics %>%
    unnest_tokens(word, lyrics) %>%
    anti_join(stop_words) %>%
    count(word, sort = TRUE)
}


```

## Topic Modeling
```{r}
## Insert code here
```

## Visualisation
Sentiment Trend Plots: Use ggplot2 to create plots of sentiment scores.
Theme Comparison Plots: Compare sentiment and thematic trends using bar and 
line plots.
Word Clouds: Use wordcloud2 to visualize prominent words for each generation.
```{r}
# Insert code here
```

